The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine Cells as Calibrators\altaffilmark{1}

### 2016-03-02 telluric/ms.tex
First finished draft on tellurics introduction except for the last paragraph.

Traditionally, telluric contamination is not considered as problematic
for precise RV in the optical. It is certainly a sever source of
spectral contamination and a bottleneck for achieving higher RV
precision in the near infra-red region (e.g.,
\citealt{2010ApJ...713..410B}), where a large number of deep water and
methane lines reside. However, there is only a small wavelength
range in the optical that has deep telluric lines, and typically such
regions are simply thrown out for the purpose of precise RV analysis,
either by giving them zero weights in the cross correlation masks (for
ThAr calibrated spectra, e.g., \citealt{2002A&A...388..632P}) or
flagging them as bad pixels (for iodine calibrated spectra, e.g., for
Keck/HIRES).

Recently, the works by \cite{artigau2014} and \cite{cunha2014} have
characterized and mitigated the effects of telluric contamination in
the precise RV data taken by the ThAr-calibrated HARPS-S.
\cite{cunha2014} focuses on the issues with ``micro-telluric" lines
(shallow telluric absorption lines with $<1$-3\% depths), which are
recognized for the first time. \cite{cunha2014} fit and then divide
out the telluric lines in the observed spectra using synthetic
telluric spectra generated by the LBLRTM package (Line-By-Line
Radiative Transfer Model, \citealt{lblrtm}; with line lists from
HIgh-resolution TRANsmission molecular absorption database, or HITRAN,
\citealt{hitran2013}) and also TAPAS \citep{tapas}, which is a more
user-friendly but less flexible package wrapper using LBLRTM. They
concluded that the micro-tellurics have an impact (defined as RMS of
difference between RVs before and after micro-telluric removal) of
$\sim$10-20 cm/s for G stars observed with low to moderate air masses,
but the impact can be substantial in some cases to up to $\sim$0.5-1
m/s. \cite{artigau2014} uses principal component analysis (PCA) to
empirically correct for telluric lines in HARPS-S data (both
micro-tellurics and the deep lines in the $\sim$630~nm region), and
combined PCA with rejection masking, they reduced the RV RMS by
$\sim$20~cm/s (and more significantly for the $\sim$630~nm region).

% I'm here:
This paper focuses on the adverse effects of telluric contamination
and its remedies under the context of iodine-calibrated precise RV,
especially for ``micro-telluric" lines (shallow telluric absorption
lines with $<1$-3\% depths; \citealt{cunha2014}). As for spectral
region contaminated with deep telluric lines, typical precise RV
analysis usually gives

Previously, \cite{cunha2014} have characterized the effects of
micro-telluric contamination and proposed solution for the
ThAr-calibrated HARPS-S data.

Modeling telluric lines itself is a challeging task. ZZZ Cite the
paper TERRASPEC and simular softwares and their 2\% modeling
precision. Cite Lockwood, Bender et al.\ for 1\% in L band. ZZZ

In this paper, we characterize and discuss the remedies for
micro-telluric lines in the context of iodine-calibarted precise
RVs. We first quantify the effects of micro-telluric contamination on
RV precision through simulation. Then we discuss possible remedies and
their effectiveness. Finally we discuss implementation on real data
and future work.

\begin{comment}
Jason's suggestions:
- run tau Ceti as target #2
- don't show our classic before+after+difference RV vs. BC, just show
the difference, especially the talk
- show actual data for sig Dra RV vs. BC of Keck, to show that this is
real, it should be standard to plot RV vs. BC to check systematics
(i.e. tellurics)
- Mention Vogt APF paper sig Dra planet.
\end{comment}

>>>>

Traditionally, telluric contamination is not considered as problematic
for precise RV in the optical. It is certainly a sever source of
spectral contamination and a bottleneck for achieving higher RV
precision in the near infra-red (NIR) region (e.g.,
\citealt{2010ApJ...713..410B}), where a large number of deep water and
methane lines reside. However, there is only a small wavelength
range in the optical that has deep telluric lines, and typically such
regions are simply thrown out for the purpose of precise RV analysis,
either by giving them zero weights in the cross correlation masks (for
ThAr calibrated spectra, e.g., \citealt{2002A&A...388..632P}) or
flagging them as bad pixels (for iodine calibrated spectra, e.g., for
Keck/HIRES).

Recently, the works by \cite{artigau2014} and \cite{cunha2014} have
characterized and mitigated the effects of telluric contamination in
the precise RV data taken by the ThAr-calibrated HARPS-S.
\cite{cunha2014} focuses on the issues with ``micro-telluric" lines
(shallow telluric absorption lines with $<1$-3\% depths), which are
recognized for the first time. \cite{cunha2014} fit and then divide
out the telluric lines in the observed spectra using synthetic
telluric spectra generated by the LBLRTM package (Line-By-Line
Radiative Transfer Model, \citealt{lblrtm}; with line lists from
HIgh-resolution TRANsmission molecular absorption database, or HITRAN,
\citealt{hitran2013}) and also TAPAS \citep{tapas}, which is a more
user-friendly but less flexible package wrapper using LBLRTM. They
concluded that the micro-tellurics have an impact (defined as RMS of
difference between RVs before and after micro-telluric removal) of
$\sim$10-20 cm/s for G stars observed with low to moderate air masses,
but the impact can be substantial in some cases to up to $\sim$0.5-1
m/s.

\cite{artigau2014} uses principal component analysis (PCA) to
empirically correct for telluric lines in HARPS-S data (both
micro-tellurics and the deep lines in the $\sim$630~nm region), and
combined PCA with rejection masking, they reduced the RV RMS by
$\sim$20~cm/s (and more significantly for the $\sim$630~nm
region). More recently, \cite{2016AAS...22713719S} characterized the
effects of telluric contamination and effectiveness of some typical
remedies (masking and modeling) for emission line-calibarated spectra
for the optical, broad optical (300-900~nm), and NIR. Their conclusion
for the optical region is similar to the results in \cite{artigau2014}
and \cite{cunha2014}.

This paper characterizes and corrects for the adverse effects of
telluric contamination under the context of iodine-calibrated precise
RV, especially for the micro-telluric lines. ZZZ We first describe our
methodology for characterizing the effects of tellurics in
Section~\ref{sec:method}, then... ZZZ
